\makenoidxglossaries 

\newglossaryentry{latex}
{
    name=latex,
    description={Is a mark up language specially suited 
    for scientific documents}
}

\newacronym{twrm}{TWRM}{two-wheeled robotic machine}

\newacronym{ib}{IB}{intermediate body}

\newacronym{fl}{FL}{fuzzy logic}

\newacronym{flc}{FLC}{fuzzy logic controller}

\newacronym{pd}{PD}{proportional derivative}

\newacronym{pid}{PID}{proportional integral derivative}

\newacronym{mimo}{MIMO}{multi-input multi-output}

\newacronym{twip}{T-WIP}{two-wheeled inverted pendulum}

\newglossaryentry{memfunction}
{
    name=membership function,
    description={A curve that defines how each point in the input space is mapped to a membership value (or degree of membership) between 0 and 1. The simplest membership functions are formed using straight lines. Of these, the simplest is the triangular membership function. It's nothing more than a collection of three points forming a triangle. The trapezoidal membership function has a flat top and really is just a truncated triangle curve. These straight line membership functions have the advantage of simplicity.}
}

\newglossaryentry{invpendulum}
{
    name=inverted pendulum,
    description={A pendulum that has its center of mass above its pivot point. The inverted pendulum system is a popular demonstration of using feedback control to stabilize an open-loop unstable system. }
}

\newglossaryentry{gyroscope}
{
    name=gyroscope,
    description={A device for measuring or maintaining orientation and angular velocity. MEMS gyroscopes use VSG resonating ring technology to sense rotation rate through a phenomenon known as coriolis. }
}

 
 
\newglossaryentry{telemetry}
{
    name=telemetry,
    description={An automated communications process by which measurements and other data are collected at remote or inaccessible points and transmitted to receiving equipment for monitoring.}
}

\newglossaryentry{fuzzlog}
{
    name=fuzzy logic,
    description={A form of many-valued logic in which the truth values of variables may be any real number between 0 and 1. It is employed to handle the concept of partial truth, where the truth value may range between completely true and completely false.}
}

\newglossaryentry{robctrl}
{
	name=robust control,
	description={An approach to controller design that explicitly deals with uncertainty. Robust control methods are designed to function properly provided that uncertain parameters or disturbances are found within some (typically compact) set.}
}

\newglossaryentry{transfunc}
{
	name=transfer function,
	description={A function characterizing a control system component which gives the device's output for each possible input.}
}