\chapter{Helpful Reading}

These books were helpful for providing the necessary background knowledge in the field of robotics and controls. Unlike the bibliography, they didn't necessary translate directly into solutions for the problems addressed.

\begin{enumerate}
    \item \textbf{Advanced Control of Wheeled Inverted Pendulum Systems} Li, Z., Yang, C., & Fan, L. (2012). Springer Science & Business Media.
    
    This text provided the necessary theory of dynamics and stability tailored to TWIP systems. It provides direct insight on how to derive the kinematics and dynamics of the robot, as well as providing various models optimized for specific controllers. It formulates linear and non-linear control methods, ranging from partial feedback linearization to neural methods. 
    
    
    \item \textbf{Advanced Formal Verification} Drechsler, R. (Ed.). (2004). Norwell: Kluwer Academic Publishers.
    
    This verification text provides an overview of verification problems, including ones pertaining to analog and dynamical system verification. It covers a state space equivalence checking methods as well as state space subdivision algorithms. Additionally, it describes how the system can be translated into a form that can be used by a conventional model checker.
    
    
    \item \textbf{Control of Complex Systems: Structural Constraints and Uncertainty} Zecevic, A., & Siljak, D. D. (2010).Springer Science & Business Media.
    
    This text covers Lyapunov stability and how a control law can be created to achieve globally asymptotically stable systems. It describes how to produce Lyapunov functions as well as other stability analysis techniques.  
    
    \item \textbf{Modern Robotics: Mechanics, Planning and Control} Kevin M.. Lynch, & Park, F. C. (2017). Cambridge University Press.
    
    Modern robotics provides insight on dynamics derivations, controller optimization and wheeled mobile robots basics. Terminology is defined and illustrated that is used throughout papers in robotic control.  
    
    \item \textbf{Nonlinear Dynamics and Chaos} Thompson, J. M. T., Thompson, M., & Stewart, H. B. (2002). John Wiley & Sons.
    
    This text provides an overview of highly dimensional systems represented by ODE's. The basics of stability are illustrated and geometric insight is provided. 
    
    
    
\end{enumerate}